### 2012-06-30 ack.tex
Feverish writing on chapters 2-4

So many people contributed to this dissertation that to name them all would compromise the honor of the most worthy. 
More than anyone else, I owe a debt of gratitude to my advisor, Charles Yang, 
who did some much to make this work, and me as a linguist,
into what it is now.
Gene Buckley, Mark Liberman, and Rolf Noyer, my commitee members, are to be thanked for creating an environment at Penn where a student could write this admittedly contenious dissertation. 
And though his name appears nowhere else on this document, it is hard to imagine this work could exist without Bill Labov.

My journey in linguistics begins with the mentoring of Jennifer Cole.
Steve Anderson graciously agreed to serve on my committee.
Morris Halle taught me to speak clearly and never apologize.

While so many of my fellow students at Penn have a hand in this document, 
I would like to especially thank my cohort, Toni Cook, Laurel MacKenzie, and Stefanie Brody.

@@

My gratitude also goes out to the administrative assistants at 3401 Walnut and 255 S. 36th, Lauris Olson at the Van Pelt Library, Katherine McEldoon for a helpful review of numerical cognition research, and Carly Fisher for her unflagging support and friendship.

>>>>

So many people contributed to this dissertation that to name them all would compromise the honor of the most worthy. More than anyone else, I owe a debt of gratitude to my advisor, Charles Yang, who has done so much for me as a linguist. Gene Buckley, Mark Liberman, and Rolf Noyer, my commitee members, are to be thanked for creating tan environment receptive to this admittedly contentious thesis. And though his name appears nowhere else in this document, it is hard to imagine this dissertation would exist without Bill Labov.

While so many of my fellow students at Penn have a hand in this document, I would like to especially thank Toni Cook and Laurel MacKenzie for all their support over the years. I also must thank the administrative assistants at 3401 Walnut and 255 S. 36th, Lauris Olson at the Van Pelt Library, Katherine McEldoon for a helpful review of numerical cognition research, and Carly Fisher for ten years of her unflagging friendship.

I have many debts beyond Penn. My journey in linguistics began with the careful mentoring of Jennifer Cole and Richard Sproat. Steve Anderson graciously agreed to serve on my committee. Morris Halle taught me to speak clearly, and to never apologize.

@@

### 2012-06-30 pre.tex
Feverish writing on chapters 2-4

This

>>>>

In this dissertation, I critique two such epicyclic proposals, and present solutions using independently-motivated grammatical machinery to account for the data.

The first half of this dissertation began with a suggestion from Charles Yang that the sparse nature of the lexicon might itself account for at least some phonotactic gaps. The success of the resulting study, in chapter four, led me to question the received wisdom that speakers' knowledge of phonotactic generalizations is gradient and potentially independent of the phonological system.

These results support a null hypothesis in which phonotactic knowledge is derivative of the language acquisition device and phonological processes. While I present this theory as a falsifiable scientific hypothesis, an alternative would treat this proposal as a \emph{negative heuristic}, a

guides us away from ``phonotactic grammar'' as an explanatory device.

even those who are not inclined to accept this proposal should note how much of the coverage traditionally attributed to
